---
title: "EDA - Corporate Governance and Company Performance"
author: "Conor Reid"
date: "28/5/2017"
output: pdf_document
---
Set the working directory and read in data as "spx" (not shown) and load in the required packages. 
```{r, echo=FALSE}
setwd("/Users/Conor/Google Drive/MSc/dissertation/data/processed")
spx=read.csv("spx.csv", sep=",", na.strings="#N/A N/A") 
``` 
```{r}
library(reshape)
library(stringr)
library(rpart)
library(lattice)
library(ggplot2)
vars = c("Ticker", "Tobin.s.Q", "AZS", "P.E", "EPS", "P.B", "P.EBITDA", 
                "Board.Size", "CEO.Duality", "X..Feml.Execs", 
                "X..Feml.Execs.1", "X..Wmn.on.Bd","X..Women.on.Bd", 
                "Bd.Avg.Age", "Board.Mtg.Att..", 
                "Asset", "Interest", "Tax", "ROE", "ROC",
                "Indep.Directors", "X..Indep.Dir.on.Aud.Cmte", 
                "X..Indep.Dir.on.Aud.Cmte.1", "Sz.Aud.Cmte", "Indep.Chrprsn")
```


# S&P 500
The S&P 500 is an American stock market index including market capitalization of 500 companies, listed on the NYSE or the NASDAQ. It is distinct from other indexes such as the Dow Jones etc due to its diverse constituency and weighting methodology.
*Would it be useful to look at other index's?*

Read in full data as below, and carry out some sub-setting. Set NA values. 
```{r}
spx_EDA = spx[vars]
spx_EDA[ spx_EDA == "#N/A Field Not Applicable" ] <- NA
```

Create categorical variable for Q and Z score, as per MM.
```{r}
m_TQ = median(subset(spx_EDA$Tobin.s.Q, !is.na(spx_EDA$Tobin.s.Q)))
m_AZ = median(subset(spx_EDA$AZS, !is.na(spx_EDA$AZS)))
spx_EDA$Tobin.s.Q.class = with(spx_EDA, ifelse(Tobin.s.Q >= m_TQ, 1, 2))
spx_EDA$AZS.class = with(spx_EDA, ifelse(AZS >= m_AZ, 1, 2))
```

View data types. Convert to numeric columns that need to be numeric. Parse out the actual ticker string (output hidden for clarity).
```{r, results="hide"}
sapply(spx_EDA,class)
cols.num <- c("P.B","EPS","P.E","P.EBITDA")
spx_EDA[cols.num] <- sapply(spx_EDA[cols.num],as.numeric)
sapply(spx_EDA, class)
spx_EDA$TickerID = str_split_fixed(spx_EDA$Ticker, " ", 2)[,1] #parse the ticker itself
```

\newpage
## Missing Data
Cases with missing values. Very high (254 / 500 = 50.8% loss if we discount them). 
```{r}
sum(!complete.cases(spx_EDA))
```
81 NA's for Altman Z score, (81 / 500 = 16.2%). 
```{r}
summary(spx_EDA)
```
\newpage
## Altman Z Score
Histogram of the Altman Z Score over the data. Looks to be a pretty normal distribution, albeit with some extreme outliers on either tail.

```{r, message=FALSE, warning=FALSE}
ggplot(data=spx_EDA) +
  geom_histogram( aes(AZS, ..density..), bins=40 ) +
  geom_density( aes(AZS, ..density..) ) +
  geom_rug( aes(AZS) ) +
  geom_vline(aes(xintercept=mean(AZS, na.rm=T)),  # red line is the mean
               color="red", linetype="dashed", size=1) +
  geom_vline(aes(xintercept=median(AZS, na.rm=T)),  # blue line is the median
               color="blue", linetype="dashed", size=1) +
  ggtitle("AZS Histogram")
```

\newpage
### Independant Directors and ALtman Z score
According to M&M;

> ...while an independent lead director and a financial leverage higher than 2.5 generates a higher risk of bankruptcy.

Risk of bankruptcy is measured by the Z score.

Plot below seems to support this, is it strong enough though? R squared value likely to be pretty small when a proper regression is done. 

```{r, warning=FALSE}
ggplot(data=subset(spx_EDA, !is.na(Indep.Directors)),
  aes(Indep.Directors, AZS )) +
  geom_point() +
  ggtitle("Indep.Directors and Altman Z score") +
  geom_smooth(method = "lm")
```

```{r}
table(spx_EDA$AZS.class)
```


Using the class variable for Z score. Not a significant relationship.
```{r, warning=FALSE}
boxplot(Indep.Directors~AZS.class,data=spx_EDA, main="Altman Z and Number of Indep Directors", 
        xlab="Altman Z Score class", ylab="Independant Directors")
```






\newpage
## Tobins Q
Histogram of Tobins Q over the data. Heavily skewed right, most companies have low scores. It is going to be difficult to learn rules for high performing companies? 
From M&M:

> As suggested by Creamer [14], we discretized Tobin’s Q ratio in order to obtain two classes, dividing each dataset according to its median value. In this way, a company that lies in the upper side of the median will be looked positively by the machine learning algorithms.

Median (blue) and mean (red) of Q score is shown below. Regression may not be suitable for data that has such a skewness. 
```{r, message=FALSE, warning=FALSE}
ggplot(data=spx_EDA) +
  geom_histogram( aes(Tobin.s.Q, ..density..), bins=40 ) +
  geom_density( aes(Tobin.s.Q, ..density..) ) +
  geom_rug( aes(Tobin.s.Q) ) +
  geom_vline(aes(xintercept=mean(Tobin.s.Q, na.rm=T)),  # red line is the mean
               color="red", linetype="dashed", size=1) +
  geom_vline(aes(xintercept=median(Tobin.s.Q, na.rm=T)),  # blue line is the median
               color="blue", linetype="dashed", size=1) +
  ggtitle("Tobins Q Histogram")
```

\newpage
Try taking the log of Tobins Q instead, histogram shown below. The code is emitted since its the same as previous page but used log(Tobin.s.Q) instead. Much less skewed, making regression more applicable? Is it OK to process the dependent variable like this?
```{r, message=FALSE, warning=FALSE}
ggplot(data=spx_EDA) +
  geom_histogram( aes(log(Tobin.s.Q), ..density..), bins=40 ) +
  geom_density( aes(log(Tobin.s.Q), ..density..) ) +
  geom_rug( aes(log(Tobin.s.Q)) ) +
  geom_vline(aes(xintercept=mean(log(Tobin.s.Q), na.rm=T)),  # red line is the mean
               color="red", linetype="dashed", size=1) +
  geom_vline(aes(xintercept=median(log(Tobin.s.Q), na.rm=T)),  # blue line is the median
               color="blue", linetype="dashed", size=1) +
  ggtitle("Log (Tobins Q) Histogram")
```
Poisson regression could be a good alternative to having to process the Q score directly, obviously assumes the dependent variable has a Poisson distribution.

See https://en.wikipedia.org/wiki/Poisson_distribution 

I don't think this it actually does, but Poisson regression may be more applicable here that OLS for example.

\newpage

### P.B (price to book ratio) and Q Score
A high P.B means that investors see the company as growing, low means they think the company's book value is exaggerated (http://www.investopedia.com/terms/p/price-to-bookratio.asp).

Interesting spike in Q score around the 150 P.B mark. Maybe worth further investigation?
```{r, warning=FALSE}
##P.B
ggplot(spx_EDA, aes(P.B, Tobin.s.Q) ) +
  geom_point() +
  ggtitle("Price to Book Ratio Vs. Tobins Q")
```

\newpage
Same as previous page, but showing the tickers for each data point. VRTX is a particular outlier (Vertex Pharmaceuticals Incorporated). 
```{r, warning=FALSE}
#with labels
 ggplot(spx_EDA, aes(P.B, Tobin.s.Q) ) +
    geom_point() +
    geom_text(aes(label=ifelse(P.B>100 & P.B<200 & 
                                 Tobin.s.Q>5,as.character(TickerID),'')),
                                  hjust=1.2, vjust=1)+
  ggtitle("Price to Book Ratio Vs. Tobins Q with Data Labels")
```

\newpage
### CEO Duality and Q Score
Research suggests the CEO Duality can be either a positive or negative influence on the success of a company, looks from the below that perhaps its not that big of an influence at all. No deviation in Q score based on duality.

```{r, warning=FALSE}
#no difference
ggplot(data=subset(spx_EDA, !is.na(CEO.Duality)),
  aes(CEO.Duality, Tobin.s.Q )) +
  geom_point() + geom_boxplot()+
  ggtitle("Effect of CEO Duality on Tobins Q")
```

\newpage
### Board Average Age and Q Score
Seems to be pretty normally distributed, skewed left due to some very young boards. 
```{r, message=FALSE, warning=FALSE}
#board average age
ggplot(data=spx_EDA) +
  geom_histogram( aes(Bd.Avg.Age, ..density..) ) +
  geom_density( aes(Bd.Avg.Age, ..density..) ) +
  geom_rug( aes(Bd.Avg.Age) )
```

\newpage
### Number of Female Executives and Q Score
Tobins Q and the number of female executives. Seems to cluster around the bottom left hand corner at low numbers and low performance, but cant see much to the upper right. Doesn't look like a strong relationship here anyway.

According to M&M:

> For the US components, we found a positive connection between the presence of women in the board and the company perfor- mance
 
and 

> Tobin’s Q ratio is positively influenced by the percentage women in the board

May need to look into this further.
```{r, warning=FALSE}
#female presence on board and success?
ggplot(spx_EDA, aes(Tobin.s.Q, X..Feml.Execs) ) +
  geom_point()
```

Try a boxplot with Tobins Q as a class instead of a continuous variable.
```{r}
boxplot(X..Feml.Execs~Tobin.s.Q.class,data=spx_EDA, main="Female Execs vs Tobins Q", 
        xlab="Tobins Q (Class)", ylab="Female Execs(%)")
```
Again, doesnt seem to have much influence.

Try with percentage of women on the board vs Tobins as a class.
```{r}
boxplot(X..Women.on.Bd~Tobin.s.Q.class,data=spx_EDA, main="Female on Board(%) vs Tobins Q", 
        xlab="Tobins Q (Class)", ylab="Female on board (%)")
```

Still nothing really. 

Try with percentage of women on the board vs Tobins as a continuous variable.
```{r, warning=FALSE}
#female presence on board and success?
ggplot(spx_EDA, aes(Tobin.s.Q, X..Women.on.Bd) ) +
  geom_point() +
  geom_smooth(method = "lm")
```

Makes literally no difference it seems.

\newpage
### ROC (Return on Capital) and Q Score
Below shows Q score against ROC (return on capital), subsetted to remove extreme values in both variables. Thus, below is a representation of the main cluster in the data. 

Looks to be a positive relationship between the two. Interesting, since ROC (may be) considered a bad strategy in the long term for companies (requires further investigation).

```{r, warning=FALSE}
ggplot(data=subset(spx_EDA, !is.na(ROC) & ROC<30 & ROC>0 & Tobin.s.Q < 5),
  aes(ROC, Tobin.s.Q )) +
  geom_point() +
  ggtitle("ROC and Tobins Q") +
  geom_smooth(method = "lm") 
```






\newpage
# STOXX® Europe 600
```{r, echo=FALSE, warning=FALSE}
setwd("/Users/Conor/Google Drive/MSc/dissertation/data/processed")
sxxp=read.csv("sxxp.csv", sep=",", na.strings="#N/A N/A") 
``` 

```{r}
sxxp_EDA = sxxp[vars]
sxxp_EDA[ sxxp_EDA == "#N/A Field Not Applicable" ] <- NA
sxxp_EDA$AZS.class = with(sxxp_EDA, ifelse(AZS >= m_AZ, 1, 2))
summary(sxxp_EDA)

```

### Audit committee and Altman Z Score

According to M&M:

> ...while in Western Europe that it is better to employ a larger audit committee in order to lower the bankruptcy risk

Again, result below doesnt look all that convincing but further analysis required. 

```{r, warning=FALSE}
ggplot(data=sxxp_EDA, 
  aes(AZS, Sz.Aud.Cmte )) +
  geom_point() +
  ggtitle("Audit Committee Size and Altman Z score") +
  geom_smooth(method = "lm")
```

\newpage
### Indep.Director / Former CEO and Tobin Q

According to M&M;

> For the Western European companies, the presence of an independent lead director or a former CEO in the board could be a sign of weaker performances, being negatively correlated with Tobin’s Q

Results below (take out one outlier, whose Q score is huge) seem to support this. Again, r score likely to be pretty low based on how distributed the data points are.
 
```{r, warning=FALSE}
ggplot(data=subset(sxxp_EDA, AZS<30 ), 
  aes(Indep.Directors, Tobin.s.Q )) +
  geom_point() +
  ggtitle("Indep Directors  and Tobins Q") +
  geom_smooth(method = "lm")
```

Try with AZS

```{r, warning=FALSE}
ggplot(data=sxxp_EDA, 
  aes(Indep.Directors, AZS )) +
  geom_point() +
  ggtitle("Indep Directors  and AZS") +
  geom_smooth(method = "lm")
```

Similar result.

Try with AZS class.
```{r, warning=FALSE}
boxplot(Indep.Directors~AZS.class,data=sxxp_EDA, main="Altman Z and Number of Indep Directors", 
        xlab="Altman Z Score class", ylab="Independant Directors")
```

Bit of a difference?

# STOXX Eastern Europe 300

```{r, echo=FALSE, warning=FALSE}
setwd("/Users/Conor/Google Drive/MSc/dissertation/data/processed")
eebp=read.csv("eebp.csv", sep=",", na.strings="#N/A N/A") 
``` 

```{r}
eebp_EDA = sxxp[vars]
eebp_EDA[ eebp_EDA == "#N/A Field Not Applicable" ] <- NA
eebp_EDA$AZS.class = with(eebp_EDA, ifelse(AZS >= m_AZ, 1, 2))
summary(eebp_EDA)
```

For Eastern Europe, M&M state that

> An independent chair- person is a positive factor related to Altman Z-score, for the companies from Eastern Europe.

Lets see. Try with continuous AZS first. Remove one very outlying AZS.
```{r, warning=FALSE}
ggplot(data=subset(eebp_EDA, !is.na(Indep.Chrprsn) & AZS<40),   
  aes(Indep.Chrprsn, AZS )) +
  geom_point() +
  ggtitle("Indep Chairperson  and AZS") +
  geom_boxplot()
```

Doesnt seem like much there.

Look at a table with AZS as a class?
```{r, warning=FALSE}
table(eebp_EDA$Indep.Chrprsn, eebp_EDA$AZS.class)
```


